The imprint of global magma oceans on exoplanet demographics

### 2023-01-21 src/tex/ms.tex
move text around

The planetary properties in question can only be probed with a finite precision that is specific to each exoplanet mission.
To test the detectability of a runaway greenhouse transition, we simulated several transit surveys with different designs and strategies and explored their capability to recover the trend and constrain its parameters.
We assessed this capability based on two determinants: the likelihood that the mission is able to detect the injected trend, and the precision with which it can constrain the parameters of that trend.

@@

\subsection{Statistical power of different mission designs}\label{sec:statpower_missions}
\subsubsection{Additional planet mass measurements}
The dependencies of a detection change when additional information beyond planet radii is available for the characterized planet population.
Since the planet bulk density $\rho \propto R^{-3}$, the signal is stronger when measured in bulk density instead of radius:
With an optimistic choice of geophysical parameters (see above), the average measured radius change is \SI{+15}{\percent} whereas the average density change is \SI{-33}{\percent}.
Constraining bulk densities requires planetary mass measurements.
We now examine the value of a follow-up campaign to constrain planet masses with respect to the detectability of the runaway greenhouse threshold.

@@

>>>>

The planetary properties in question can only be probed with a finite precision that is specific to each exoplanet mission.

@@

\subsection{Statistical power of different mission designs}\label{sec:statpower_missions}
To explore the impact of mission trade-offs on the detectability of the runaway greenhouse transition, we simulated several transit surveys with different designs and strategies and measured their capability to recover the trend and constrain its parameters.
We assessed this capability based on two determinants: the likelihood that the mission is able to detect the injected trend, and the precision with which it can constrain the parameters of that trend.

\subsubsection{Additional planet mass measurements}
The dependencies of a detection change when additional information beyond planet radii is available for the characterized planet population.
Since the planet bulk density $\rho \propto R^{-3}$, the signal is stronger when measured in bulk density instead of radius:
With an optimistic choice of geophysical parameters (see above), the average measured radius change is \SI{+15}{\percent} whereas the average density change is \SI{-33}{\percent}.
Constraining bulk densities requires planetary mass measurements.
We now examine the value of a follow-up campaign to constrain planet masses with respect to the detectability of the runaway greenhouse threshold.

@@

\subsubsection{Constraining the threshold instellation}
\todo[inline]{for different survey modes, compare the constraints on  $S_{thresh}$.
Plot posteriors from random draws of simulations.}
